---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# trees

<!-- badges: start -->
<!-- badges: end -->

The goal of trees is to ...

## Installation

You can install the development version of trees like so:

``` r
# FILL THIS IN! HOW CAN PEOPLE INSTALL YOUR DEV PACKAGE?
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(trees)

language <- language_r()
language_node_kind_for_id(language, 3L)

parser <- new_parser()
parser_set_language(parser, language)

tree <- parser_parse(parser, "x + 1")

root_node <- tree_root_node(tree)

node_as_text(root_node)
```

```{r cars}
sources <- language_download("tree-sitter/tree-sitter-python", "master")
dll_info <- language_build(sources)

language <- language_get("tree_sitter_python")
language_node_kind_for_id(language, 3L)

parser <- new_parser()
parser_set_language(parser, language)

parser_parse(parser, "x + 1")
```

You'll still need to render `README.Rmd` regularly, to keep `README.md` up-to-date. `devtools::build_readme()` is handy for this.

You can also embed plots, for example:

```{r pressure, echo = FALSE}
plot(pressure)
```

In that case, don't forget to commit and push the resulting figure files, so they display on GitHub and CRAN.
